Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-02-04 Draft/scanNLO.tex
Reorganise the figure folder and fixed some merged problems

Concerning leptonic kinematics, we show in Fig.~\ref{fig:mjjdyjj_1d_3} the distributions of the lepton-lepton invariant mass and of the Zeppenfeld variable of the electron \MP{We should defined the Zep var. somewhere}.

\begin{figure}[hbt]
\centering
{\includegraphics[scale=0.35]{figures/scanfigures/mll_nlo.pdf}}
{\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
\caption{NLO QCD inclusive study: distributions of the lepton--lepton invariant mass and the electron Zeppenfeld variable, obtained with full ({\sc Recola}) and approximated ({\sc VBFNLO, Bonsay}) amplitudes at order $\mathcal{O}(\alphas\alpha^6)$.} \label{fig:mjjdyjj_1d_3}
\end{figure}
{\bf GP: leptonic variables, comment further.}

>>>>

Concerning leptonic kinematics, we show in Fig.~\ref{fig:mjjdyjj_1d_3} the distributions of the lepton-lepton invariant mass and of the Zeppenfeld variable of the electron \MP{We should defined the Zep var. somewhere}.
\begin{figure}[hbt]
\centering
{\includegraphics[scale=0.35]{figures/scanfigures/mll_nlo.pdf}}
{\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
\caption{NLO QCD inclusive study: distributions of the lepton--lepton invariant mass and the electron Zeppenfeld variable, obtained with full ({\sc Recola}) and approximated ({\sc VBFNLO, Bonsay}) amplitudes at order $\mathcal{O}(\alphas\alpha^6)$.} \label{fig:mjjdyjj_1d_3}
\end{figure}
The {\sc VBFNLO} result for the $e^+\mu^+$ invariant mass agrees pretty well with the full curve, generated with {\sc Recola}; the {\sc Bonsay} curve is about 10 \% smaller. The discrepancies are roughly constant over the whole specrum.\\
Instead, the right panel of fig.~\ref{fig:mjjdyjj_1d_3} clearly shows that the Zeppenfeld variable of the positron $z_e$ is strongly affected by the exclusion of $s$--channels, with increasing discrepancy w.r.t. the full result at large values. The muon variable $z_{\mu}$ behaviour is almost identical to $z_e$.\\
